decompr: GVC decomposition in R

### 2015-01-27 draft.Rnw
fix tables

\usepackage[latin1]{inputenc}
\usepackage{rotating}
\usepackage{mathtools}
\usepackage{threeparttable}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{changepage}
\usepackage{lscape}
\usepackage[natbib, authordate, backend=biber]{biblatex-chicago}
\usepackage[hidelinks]{hyperref}

@@

\subsection{Output}
<<lt-out >>=
lt
@

We can now analyse the output which consists of a GNxGN matrix that gives for each country and industry the
value added origins of its exports by country and industry. To this end, we look at the results of the Leontief
decomposition for our example data set (Table \ref{tab:leon}). In the first column we find the source countries and
industries while the first row contains the using countries and industries. The first element, $28.52$, thus gives the
amount of value added that the Argentinian Agriculture industry has contributed to the exports of the Argentinian
Agriculture industry. Similarly, the last element of this row, $4.12$, gives the amount of value added that the
Argentinian Agriculture industry has contributed to the exports of the German Transport Equipment industry.

@@

\newpage
\begin{table}[htbp] \scriptsize
    \begin{adjustwidth}{-1.15in}{-1.15in}  
  \centering
  \caption{Leontief Decomposition}
    \begin{tabular}{lccccccccc}
    \toprule
          & Argentina. & Argentina. & Argentina. & Turkey. & Turkey. & Turkey. & Germany. & Germany. & Germany.\\
          & Agriculture & Textile.and. & Transport. & Agriculture & Textile.and. & Transport. & Agriculture & Textile.and. & Transport.\\
          & & Leather & Equipment & & Leather & Equipment & & Leather & Equipment\\
    \midrule
    Argentina.Agriculture & 28.52 & 2.79  & 0.36  & 1.81  & 3.12  & 0.36  & 1.24  & 1.30  & 4.12 \\
    Argentina.Textile.and.Leather & 1.06  & 19.12 & 0.42  & 0.48  & 1.83  & 0.43  & 0.59  & 1.15  & 4.75 \\
    Argentina.Transport.Equipment & 0.21  & 0.14  & 1.06  & 0.03  & 0.08  & 0.04  & 0.02  & 0.07  & 0.19 \\
    Turkey.Agriculture & 0.72  & 1.34  & 0.12  & 34.93 & 7.00  & 1.48  & 2.55  & 1.52  & 6.18 \\
    Turkey.Textile.and.Leather & 0.41  & 1.39  & 0.12  & 2.69  & 40.17 & 1.32  & 1.11  & 1.15  & 9.51 \\
    Turkey.Transport.Equipment & 0.03  & 0.09  & 0.03  & 0.81  & 0.91  & 3.16  & 0.12  & 0.07  & 0.65 \\
    Germany.Agriculture & 0.93  & 2.25  & 0.16  & 2.31  & 2.06  & 0.51  & 29.88 & 5.25  & 9.60 \\
    Germany.Textile.and.Leather & 0.65  & 0.73  & 0.08  & 1.54  & 2.55  & 0.63  & 1.46  & 18.96 & 8.16 \\
    Germany.Transport.Equipment & 0.67  & 0.65  & 0.26  & 1.29  & 1.49  & 0.57  & 1.73  & 1.51  & 34.74 \\
    \bottomrule
    \end{tabular}
  \label{tab:leon}
      \end{adjustwidth}
\end{table}

\begin{table}[htbp]\scriptsize
    \begin{adjustwidth}{-1.15in}{-1.15in} 
  \centering
  \caption{Non-decomposed Values}
    \begin{tabular}{lccccccccc}
    \toprule
         & Argentina. & Argentina. & Argentina. & Turkey. & Turkey. & Turkey. & Germany. & Germany. & Germany.\\
          & Agriculture & Textile.and. & Transport. & Agriculture & Textile.and. & Transport. & Agriculture & Textile.and. & Transport.\\
          & & Leather & Equipment & & Leather & Equipment & & Leather & Equipment\\
    \midrule
    Argentina.Agriculture & 6.88  & 2.49  & 0.25  & 1.30  & 2.04  & 0.08  & 0.77  & 0.68  & 1.76 \\
    Argentina.Textile.and.Leather & 1.03  & 3.91  & 0.44  & 0.04  & 1.52  & 0.31  & 0.30  & 0.95  & 4.13 \\
    Argentina.Transport.Equipment & 0.38  & 0.24  & 0.55  & 0.00  & 0.05  & 0.06  & 0.00  & 0.10  & 0.18 \\
    Turkey.Agriculture & 0.47  & 0.93  & 0.03  & 7.33  & 6.27  & 1.20  & 2.23  & 0.75  & 3.19 \\
    Turkey.Textile.and.Leather & 0.13  & 1.37  & 0.01  & 2.48  & 13.35 & 1.24  & 0.52  & 0.61  & 9.19 \\
    Turkey.Transport.Equipment & 0.00  & 0.05  & 0.04  & 1.67  & 1.52  & 1.75  & 0.05  & 0.00  & 0.65 \\
    Germany.Agriculture & 0.51  & 2.05  & 0.04  & 1.67  & 0.57  & 0.12  & 7.18  & 4.73  & 6.43 \\
    Germany.Textile.and.Leather & 0.56  & 0.54  & 0.00  & 1.30  & 2.28  & 0.51  & 1.26  & 7.06  & 8.65 \\
    Germany.Transport.Equipment & 0.90  & 0.68  & 0.41  & 1.67  & 1.47  & 0.77  & 2.80  & 1.96  & 18.42 \\
    \bottomrule
    \end{tabular}
  \label{tab:noleon}
        \end{adjustwidth}
\end{table}

@@

    \begin{adjustwidth}{-1.15in}{-1.15in}

@@

    \begin{tabular}{lccccccccccccccc}

@@

    exporter.exportingind.importer & DVA\_FIN & DVA\_INT & DVA\_INTrexI1 & DVA\_INTrexF & DVA\_INTrexI2 & RDV\_INT & RDV\_FIN & RDV\_FIN2 & OVA\_FIN & MVA\_FIN & OVA\_INT & MVA\_INT & DDC\_FIN & DDC\_INT & ODC \\

@@

  \end{adjustwidth}

@@

>>>>

\usepackage[latin1]{inputenc}
\usepackage{rotating}
\usepackage{adjustbox}
\usepackage{mathtools}
\usepackage{threeparttable}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{changepage}
\usepackage{lscape}
\usepackage{pbox}
\usepackage{array}
\usepackage[natbib, authordate, backend=biber]{biblatex-chicago}
\usepackage[hidelinks]{hyperref}

\newcolumntype{R}[2]{
    >{\adjustbox{angle=#1,lap=\width-(#2)}\bgroup}
    l
    <{\egroup}
}
\newcommand*\rot{\multicolumn{1}{R{45}{1em}}}
\newcommand*\rotnt{\multicolumn{1}{R{90}{1em}}}

@@

\subsection{Output}
We can now analyse the output which consists of a GNxGN matrix that gives for each country and industry the
value added origins of its exports by country and industry. To this end, we look at the results of the Leontief
decomposition for our example data set (Table \ref{tab:leon}). In the first column we find the source countries and
industries while the first row contains the using countries and industries. The first element, $28.52$, thus gives the
amount of value added that the Argentinian Agriculture industry has contributed to the exports of the Argentinian
Agriculture industry. Similarly, the last element of this row, $4.12$, gives the amount of value added that the
Argentinian Agriculture industry has contributed to the exports of the German Transport Equipment industry.

@@

\newpage
\begin{landscape}

\begin{table}[htbp] \scriptsize
%    \begin{adjustwidth}{-1.15in}{-1.15in}  
%  \centering
  \caption{Leontief Decomposition}
  \label{tab:leon}
  \begin{tabular}{lccccccccc}
    \toprule
          & Argentina. & Argentina. & Argentina. & Turkey. & Turkey. & Turkey. & Germany. & Germany. & Germany.\\
          & Agriculture & Textile.and. & Transport. & Agriculture & Textile.and. & Transport. & Agriculture & Textile.and. & Transport.\\
          & & Leather & Equipment & & Leather & Equipment & & Leather & Equipment\\
    \midrule
    Argentina.Agriculture & 28.52 & 2.79  & 0.36  & 1.81  & 3.12  & 0.36  & 1.24  & 1.30  & 4.12 \\
    Argentina.Textile.and.Leather & 1.06  & 19.12 & 0.42  & 0.48  & 1.83  & 0.43  & 0.59  & 1.15  & 4.75 \\
    Argentina.Transport.Equipment & 0.21  & 0.14  & 1.06  & 0.03  & 0.08  & 0.04  & 0.02  & 0.07  & 0.19 \\
    Turkey.Agriculture & 0.72  & 1.34  & 0.12  & 34.93 & 7.00  & 1.48  & 2.55  & 1.52  & 6.18 \\
    Turkey.Textile.and.Leather & 0.41  & 1.39  & 0.12  & 2.69  & 40.17 & 1.32  & 1.11  & 1.15  & 9.51 \\
    Turkey.Transport.Equipment & 0.03  & 0.09  & 0.03  & 0.81  & 0.91  & 3.16  & 0.12  & 0.07  & 0.65 \\
    Germany.Agriculture & 0.93  & 2.25  & 0.16  & 2.31  & 2.06  & 0.51  & 29.88 & 5.25  & 9.60 \\
    Germany.Textile.and.Leather & 0.65  & 0.73  & 0.08  & 1.54  & 2.55  & 0.63  & 1.46  & 18.96 & 8.16 \\
    Germany.Transport.Equipment & 0.67  & 0.65  & 0.26  & 1.29  & 1.49  & 0.57  & 1.73  & 1.51  & 34.74 \\
    \bottomrule
    \end{tabular}

%      \end{adjustwidth}
% \end{table}
% 
% \begin{table}[htbp]\scriptsize
%    \begin{adjustwidth}{-1.15in}{-1.15in}

\medskip
%  \centering
  \caption{Non-decomposed Values}
  \label{tab:noleon}
  \begin{tabular}{lrrrrrrrrr}
    \toprule
         & Argentina. & Argentina. & Argentina. & Turkey. & Turkey. & Turkey. & Germany. & Germany. & Germany.\\
          & Agriculture & Textile.and. & Transport. & Agriculture & Textile.and. & Transport. & Agriculture & Textile.and. & Transport.\\
          & & Leather & Equipment & & Leather & Equipment & & Leather & Equipment\\
    \midrule
    Argentina.Agriculture & 6.88  & 2.49  & 0.25  & 1.30  & 2.04  & 0.08  & 0.77  & 0.68  & 1.76 \\
    Argentina.Textile.and.Leather & 1.03  & 3.91  & 0.44  & 0.04  & 1.52  & 0.31  & 0.30  & 0.95  & 4.13 \\
    Argentina.Transport.Equipment & 0.38  & 0.24  & 0.55  & 0.00  & 0.05  & 0.06  & 0.00  & 0.10  & 0.18 \\
    Turkey.Agriculture & 0.47  & 0.93  & 0.03  & 7.33  & 6.27  & 1.20  & 2.23  & 0.75  & 3.19 \\
    Turkey.Textile.and.Leather & 0.13  & 1.37  & 0.01  & 2.48  & 13.35 & 1.24  & 0.52  & 0.61  & 9.19 \\
    Turkey.Transport.Equipment & 0.00  & 0.05  & 0.04  & 1.67  & 1.52  & 1.75  & 0.05  & 0.00  & 0.65 \\
    Germany.Agriculture & 0.51  & 2.05  & 0.04  & 1.67  & 0.57  & 0.12  & 7.18  & 4.73  & 6.43 \\
    Germany.Textile.and.Leather & 0.56  & 0.54  & 0.00  & 1.30  & 2.28  & 0.51  & 1.26  & 7.06  & 8.65 \\
    Germany.Transport.Equipment & 0.90  & 0.68  & 0.41  & 1.67  & 1.47  & 0.77  & 2.80  & 1.96  & 18.42 \\
    \bottomrule
    \end{tabular}

%        \end{adjustwidth}
\end{table}
\end{landscape}

@@

%    \begin{adjustwidth}{-1.15in}{-1.15in}

@@

    \begin{tabular}{lrrrrrrrrrrrrrrr}

@@

    exporter.exportingind.importer & \rot{DVA\_FIN} & \rot{DVA\_INT} & \rot{DVA\_INTrexI1} & \rot{DVA\_INTrexF} & \rot{DVA\_INTrexI2} & \rot{RDV\_INT} & \rot{RDV\_FIN} & \rot{RDV\_FIN2} & \rot{OVA\_FIN} & \rot{MVA\_FIN} & \rot{OVA\_INT} & \rot{MVA\_INT} & \rot{DDC\_FIN} & \rot{DDC\_INT} & \rot{ODC} \\

@@

%  \end{adjustwidth}

@@

\appendix

\section{Tables}

\begin{table}[hb!]
\scriptsize
\centering
\caption{Input Data}
\label{tab:leather}
\begin{tabular}{llrrrrrrrrrrrrrr}
  \hline
%&  & Argentina & Argentina & Argentina & Turkey & Turkey & Turkey & Germany & Germany & Germany & Argentina & Turkey & Germany &  \\
%        countries& industries & Agriculture & Textile.and. & Transport. & Agriculture & Textile.and. & Transport. & Agriculture & Textile.and. & Transport. & final & final & final & output\\
%         & & & Leather & Equipment & & Leather & Equipment & & Leather & Equipment\\
         & & \multicolumn{3}{c}{Argentina} & \multicolumn{3}{c}{Turkey} & \multicolumn{3}{c}{Germany} & \multicolumn{3}{c}{Final Demand} & Output \\
\hline
Country & Industry & \rotnt{\pbox{4cm}{Agriculture}} & \rotnt{\pbox{4cm}{Textile and\\ Leather}} & \rotnt{\pbox{4cm}{Transport\\ Equipment}} & \rotnt{\pbox{4cm}{Agriculture}} & \rotnt{\pbox{4cm}{Textile and\\ Leather}} & \rotnt{\pbox{4cm}{Transport\\ Equipment}} & \rotnt{\pbox{4cm}{Agriculture}} & \rotnt{\pbox{4cm}{Textile and\\ Leather}} & \rotnt{\pbox{4cm}{Transport\\ Equipment}} & \rotnt{Argentina} & \rotnt{Turkey} & \rotnt{Germany} \\
\hline
Argentina & Agriculture & 16.1 & 5.1 & 1.8 & 3.2 & 4.3 & 0.4 & 3.1 & 2.8 & 4.9 & 21.5 & 6.1 & 8.4 & 77.7 \\ 
Argentina & Textile.and.Leather & 2.4 & 8 & 3.2 & 0.1 & 3.2 & 1.6 & 1.2 & 3.9 & 11.5 & 16.2 & 1.9 & 5.1 & 58.3 \\ 
Argentina & Transport.Equipment & 0.9 & 0.5 & 4 & 0 & 0.1 & 0.3 & 0 & 0.4 & 0.5 & 11 & 0.5 & 0.8 & 19 \\ 
Turkey & Agriculture & 1.1 & 1.9 & 0.2 & 18 & 13.2 & 6.1 & 9 & 3.1 & 8.9 & 7.5 & 29.5 & 14.2 & 112.7 \\ 
Turkey & Textile.and.Leather & 0.3 & 2.8 & 0.1 & 6.1 & 28.1 & 6.3 & 2.1 & 2.5 & 25.6 & 8.9 & 24.9 & 16.9 & 124.6 \\ 
Turkey & Transport.Equipment & 0 & 0.1 & 0.3 & 4.1 & 3.2 & 8.9 & 0.2 & 0 & 1.8 & 1.2 & 18.5 & 4.9 & 43.2 \\ 
Germany & Agriculture & 1.2 & 4.2 & 0.3 & 4.1 & 1.2 & 0.6 & 29 & 19.5 & 17.9 & 9.2 & 17.9 & 51.2 & 156.3 \\ 
Germany & Textile.and.Leather & 1.3 & 1.1 & 0 & 3.2 & 4.8 & 2.6 & 5.1 & 29.1 & 24.1 & 7.9 & 10.1 & 38.5 & 127.8 \\ 
Germany & Transport.Equipment & 2.1 & 1.4 & 3 & 4.1 & 3.1 & 3.9 & 11.3 & 8.1 & 51.3 & 25.1 & 35.2 & 68.4 & 217 \\ 
   \hline
\end{tabular}
\end{table}
\end{landscape}

### 2015-01-27 draft.tex
fix tables

\subsection{Output}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{lt}
\end{alltt}
\begin{verbatim}
##                               Argentina.Agriculture
## Argentina.Agriculture                   28.52278143
## Argentina.Textile.and.Leather            1.06206936
## Argentina.Transport.Equipment            0.21043693
## Turkey.Agriculture                       0.71952151
## Turkey.Textile.and.Leather               0.41201175
## Turkey.Transport.Equipment               0.03482652
## Germany.Agriculture                      0.92530356
## Germany.Textile.and.Leather              0.64666560
## Germany.Transport.Equipment              0.66638333
##                               Argentina.Textile.and.Leather
## Argentina.Agriculture                            2.79395126
## Argentina.Textile.and.Leather                   19.12053186
## Argentina.Transport.Equipment                    0.14228369
## Turkey.Agriculture                               1.34237213
## Turkey.Textile.and.Leather                       1.38523849
## Turkey.Transport.Equipment                       0.08553139
## Germany.Agriculture                              2.25142713
## Germany.Textile.and.Leather                      0.72785683
## Germany.Transport.Equipment                      0.65080723
##                               Argentina.Transport.Equipment
## Argentina.Agriculture                            0.35606694
## Argentina.Textile.and.Leather                    0.41813924
## Argentina.Transport.Equipment                    1.06369578
## Turkey.Agriculture                               0.11504126
## Turkey.Textile.and.Leather                       0.11764036
## Turkey.Transport.Equipment                       0.02667530
## Germany.Agriculture                              0.16222512
## Germany.Textile.and.Leather                      0.08244379
## Germany.Transport.Equipment                      0.25807221
##                               Turkey.Agriculture
## Argentina.Agriculture                 1.81066955
## Argentina.Textile.and.Leather         0.48370042
## Argentina.Transport.Equipment         0.03329456
## Turkey.Agriculture                   34.92704803
## Turkey.Textile.and.Leather            2.69291816
## Turkey.Transport.Equipment            0.81210167
## Germany.Agriculture                   2.31122022
## Germany.Textile.and.Leather           1.53837777
## Germany.Transport.Equipment           1.29066963
##                               Turkey.Textile.and.Leather
## Argentina.Agriculture                          3.1173841
## Argentina.Textile.and.Leather                  1.8329024
## Argentina.Transport.Equipment                  0.0790545
## Turkey.Agriculture                             6.9994970
## Turkey.Textile.and.Leather                    40.1671410
## Turkey.Transport.Equipment                     0.9075189
## Germany.Agriculture                            2.0595825
## Germany.Textile.and.Leather                    2.5488967
## Germany.Transport.Equipment                    1.4880228
##                               Turkey.Transport.Equipment
## Argentina.Agriculture                         0.35901126
## Argentina.Textile.and.Leather                 0.43058635
## Argentina.Transport.Equipment                 0.04024626
## Turkey.Agriculture                            1.47711579
## Turkey.Textile.and.Leather                    1.31799873
## Turkey.Transport.Equipment                    3.16041392
## Germany.Agriculture                           0.51211484
## Germany.Textile.and.Leather                   0.63316614
## Germany.Transport.Equipment                   0.56934671
##                               Germany.Agriculture
## Argentina.Agriculture                   1.2364172
## Argentina.Textile.and.Leather           0.5937041
## Argentina.Transport.Equipment           0.0231846
## Turkey.Agriculture                      2.5543089
## Turkey.Textile.and.Leather              1.1093993
## Turkey.Transport.Equipment              0.1151191
## Germany.Agriculture                    29.8763359
## Germany.Textile.and.Leather             1.4593583
## Germany.Transport.Equipment             1.7321726
##                               Germany.Textile.and.Leather
## Argentina.Agriculture                          1.30283802
## Argentina.Textile.and.Leather                  1.15375958
## Argentina.Transport.Equipment                  0.07482343
## Turkey.Agriculture                             1.52213499
## Turkey.Textile.and.Leather                     1.15207241
## Turkey.Transport.Equipment                     0.07448266
## Germany.Agriculture                            5.24719728
## Germany.Textile.and.Leather                   18.95868110
## Germany.Transport.Equipment                    1.51401054
##                               Germany.Transport.Equipment
## Argentina.Agriculture                           4.1208736
## Argentina.Textile.and.Leather                   4.7490351
## Argentina.Transport.Equipment                   0.1932621
## Turkey.Agriculture                              6.1806254
## Turkey.Textile.and.Leather                      9.5069032
## Turkey.Transport.Equipment                      0.6464733
## Germany.Agriculture                             9.6006931
## Germany.Textile.and.Leather                     8.1583150
## Germany.Transport.Equipment                    34.7438192
\end{verbatim}
\end{kframe}
\end{knitrout}

We can now analyse the output which consists of a GNxGN matrix that gives for each country and industry the
value added origins of its exports by country and industry. To this end, we look at the results of the Leontief
decomposition for our example data set (Table \ref{tab:leon}). In the first column we find the source countries and
industries while the first row contains the using countries and industries. The first element, $28.52$, thus gives the
amount of value added that the Argentinian Agriculture industry has contributed to the exports of the Argentinian
Agriculture industry. Similarly, the last element of this row, $4.12$, gives the amount of value added that the
Argentinian Agriculture industry has contributed to the exports of the German Transport Equipment industry.

>>>>

\subsection{Output}
We can now analyse the output which consists of a GNxGN matrix that gives for each country and industry the
value added origins of its exports by country and industry. To this end, we look at the results of the Leontief
decomposition for our example data set (Table \ref{tab:leon}). In the first column we find the source countries and
industries while the first row contains the using countries and industries. The first element, $28.52$, thus gives the
amount of value added that the Argentinian Agriculture industry has contributed to the exports of the Argentinian
Agriculture industry. Similarly, the last element of this row, $4.12$, gives the amount of value added that the
Argentinian Agriculture industry has contributed to the exports of the German Transport Equipment industry.
